---
title: "workthrough"
author: "Misha Leong"
date: "1/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Individual Species EDA

The goal of this is to focus in on individual species in iNat to look for cool patterns.  First, I"m going to utliize the dataset from CNC, but eventually I"m going to pull out patterns directly from the iNaturalist database.

```{r loadup}
# load libraries
library(tidyverse)
library(vegan)
library(ggmap)
library(ggrepel)
library(ggpubr)
library(stringr)

# load files
load('data/all_inat.Rdata')
load('data/cities.Rdata')
```

## Iniitial look

```{r CNC}
sp <- all_inat %>%
  filter(scientific_name == "Capsella bursa-pastoris") %>%
  group_by(hometown) %>%
  summarise(count = n())
sp
```
```{r newData}
library (rinat)
sp <- get_inat_obs(taxon_name = "Capsella bursa-pastoris", quality = "research",
                       maxresults = 99999)
```
There are 2656 records of shepherd's purse. Next, map these and link them to
NLCD data to look at increasing urbanizaiton intensity linkage.
